Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-08-27 prop_letter.tex
prop_letter.tex \section{Kochen-Specker} Updating the proof...

\amr{Fix below until next marker}
If a QIVPM is 0-deterministic, then for a family of $M$ commuting
observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$, we can prove
that the product of expectation values of the individual observables
relative to $\bar{\mu}$ is the expectation value of the product of the
family relative to $\bar{\mu}$:
\begin{equation}
\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
\end{equation}
If the QIVPM $\bar{\mu}$ is 0-deterministic, the expectation value of
each observable $\mathbf{O}_j$ given by
Eq.~(\ref{eq:quantum-interval-expectation-core}) collapses to a single
point

this interval collapses
to a singleton $\left\{ \lambda\right\} $, where $\lambda$ is an
eigenvalue of~$\mathbf{O}$.

@@

When $\delta \ge \frac{1}{3}$, the situation abruptly
changes. Assuming a Hilbert space $\Hilb$ of dimension $d \ge 3$, then
for any projector $P$ that projects onto an $n$-dimensional subspace
of $\Hilb$, it is straightforward to check that
$\bar{\mu}\left(P\right)=\left[n/3,n/3\right]$ is a valid
$\frac{1}{3}$-deterministic QIVPM.

>>>>

\amr{Fix below until next marker}

If a QIVPM~$\bar{\mu}$ is 0-deterministic, then for a family of
$M$ commuting observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$,
they can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$.
By restricting to the commuting subspace of events~$\set{\sum_{\ket{k}\in E}\proj{k}}{E\subseteq\Omega}$,
the quantum expectation values of the observables~$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$
and the product observables~$\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}$
are equal to the Choquet integral of the corresponding random variables
relative to the 0-deterministic classical IVPM~$\bar{\mu}'$ corresponding
to $\bar{\mu}$. The Choquet integral relative to 0-deterministic
$\bar{\mu}'$ is a singleton set. If we adopt the product rule of
singleton sets, $\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{ x_{0}x_{1}\right\} $,
we can can prove that the product of expectation values of the individual
observables relative to $\bar{\mu}$ is the expectation value of the
product of the family relative to $\bar{\mu}$~\citep{HOSTunpublished}:
\begin{equation}
\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
\end{equation}
because the Choquet integral relative to 0-deterministic $\bar{\mu}'$
has the corresponding property.

@@

When $\delta \ge \frac{1}{3}$, the situation abruptly
changes. Assuming a Hilbert space $\Hilb$ of dimension $3$, then
for any projector $P$ that projects onto an $n$-dimensional subspace
of $\Hilb$, it is straightforward to check that
$\bar{\mu}\left(P\right)=\left[n/3,n/3\right]$ is a valid
$\frac{1}{3}$-deterministic QIVPM.
